Stochastic blockmodeling of relational event dynamics

### 2012-06-01 docs/experiments.tex
Update results tables.

\begin{itemize}
%\item Kiel email: \cite{Ebel2002}
\item Classroom \cite{McFarland2001}: 445 directed communication among 27 people a high
  school classroom collected via participant observation ($M_{test}= 145$).
\item University email \cite{Eckmann2004}: 3300 dyadic emails among 88 people with at least 30
  emails each ($M_{test} = 1300$)
\item Enron email \cite{Klimt2004}: 4000 dyadic emails among 141
  individuals between TODO months ($M_{test} = 1000$)
%\item Irvine: dyadic interactions among 401 actors each having more than 30 events,  \cite{Opsahl}
\item Twitter direct messages: Tweets from Twitter.com occurring between from May 11, 2009 to January 26, 2012 that contained the hashtag \texttt{\#rstats}.  This hashtag is used to denote messages pertaining to the R statistical computing environment and sometimes statistical discussion more generally.  We collect dyadic events by selecting tweets beginning with the \texttt{@} symbol (called a \emph{mention}), and mark the first mentioned user as the recipient.
Of 28337 total tweets in this time period, 3926 were directed events among a total of 1079 users.
We use a subset 4330 events among 487 users who participated in more than one event ($M_{test} = 1330$).\footnote{This dataset will be made publicly available.}
\item MIT Reality Mining \cite{Eagle2009}: 2000 phone calls among the 89 recipients between the dates TODO ($M_{test}= 1000$).
\end{itemize}

@@

{ \footnotesize
\input{../figs/results-llk4.tex}
\input{../figs/results-recall-5.tex}
\input{../figs/results-recall-20.tex}
}
%\subsection{Baselines}

>>>>

\begin{itemize}
%\item Kiel email: \cite{Ebel2002}
\item Classroom \cite{McFarland2001}: 445 directed communication among 27 people a high
  school classroom collected via participant observation ($M_{test}= 145$).
\item University email \cite{Eckmann2004}: 3300 dyadic emails among 88 people with at least 30
  emails each ($M_{test} = 1300$)
\item Enron email \cite{Klimt2004}: 4000 dyadic emails among 141
  individuals between July 2001 and August 2001 ($M_{test} = 1000$)
%\item Irvine: dyadic interactions among 401 actors each having more than 30 events,  \cite{Opsahl}
\item Twitter direct messages: Tweets from Twitter.com occurring between from May 11, 2009 to January 26, 2012 that contained the hashtag \texttt{\#rstats}.  This hashtag is used to denote messages pertaining to the R statistical computing environment and sometimes statistical discussion more generally.  We collect dyadic events by selecting tweets beginning with the \texttt{@} symbol (called a \emph{mention}), and mark the first mentioned user as the recipient.
Of 28337 total tweets in this time period, 3926 were directed events among a total of 1079 users.
We use a subset 4330 events among 487 users who participated in more than one event ($M_{test} = 1330$).\footnote{This dataset will be made publicly available.}
\item MIT Reality Mining \cite{Eagle2009}: 2000 phone calls among the
  89 recipients between October 2001 and February 2002 ($M_{test}= 1000$).
\end{itemize}

@@

{ \scriptsize
\input{../figs/results-llk4.tex}
\input{../figs/results-recall-all.tex}
}
%\subsection{Baselines}
